### 2017-07-04 Blog/06-WhatIsMass.tex
Better summary

TL;DR The inertial mass tells us how many states are there within a given range of trajectories. More massive bodies are harder to accelerate because they have to go through more states to reach the same change in trajectory.

>>>>

TL;DR Inertial mass tells us how many states are there within a given range of velocity. More massive bodies are harder to accelerate because they have to go through more states to reach the same change in velocity.
